### 2011-11-01 paper.tex
typo

\noindent
\begin{tabular}{ll}
Symbol & Meaning \\
\hline
$\grammar$ & Grammar \\
$\nodelabels$ & Set of node labels \\
$\terminals$ & Set of terminals \\
$\rules$ & Set of transformation rules \\
$\rulesubset{n}{A}$ & Set of transformation rules of type $n$ (see \tabref{RuleTypes}) whose LHS is $((\beta)A)\alpha$ \\
$\alpha,\beta$ & Arbitrary ordered node-labeled trees \\
$\weight$ & Rule weight function \\
$\seqweight{\alpha}{\outseq}$ & Sum, over derivations of $\outseq$ from $\alpha$, of product over derivation rule weights \\
$\epsilon$ & The empty string \\
$\terminals^\ast$ & Set of strings over $\terminals$, including the empty string \\
$\outseq$ & Output sequence \\
$|\outseq|$ & Length of $\outseq$ \\
$i,j,k,l$ & Integer co-ordinates on $\outseq$, with $1 \leq i \leq j \leq k \leq l \leq |\outseq|$ \\
$m,n$ & Integer co-ordinates on $\outseq$, with $i \leq m \leq j$ and $k \leq n \leq l$ \\
$\outerlen, \innerlen$ & Integer lengths of $\outseq$-subsequences, with $0 \leq \innerlen = (k-j) \leq \outerlen = (l-i) \leq |\outseq|$ \\
$\outsubseq{i}{i}$ & The empty string \\
$\outsubseq{i}{j}$ & (For $j \geq i$) Substring of $\outseq$ from $i$ to $j-1$ inclusive \\
$\match(i,j,x)$ & Indicates if rule string $x$ matches output string $\outsubseq{i}{j}$ \\
$\fmatch(i,x)$ & Indicates if rule string $x$ matches output string $\outseq$, starting at position $i$ \\
$\rmatch(j,y)$ & Indicates if rule string $y$ matches output string $\outseq$, ending before position $j$ \\
$\iumatch,\jvmatch,\kxmatch,\lymatch$ & Rule string matchers; $\match_{ns}$ matches string $s$ ending/starting at position $n$ \\
$\m(i,j,k,l,A)$ & Inside weight for $\outsubseq{i}{j}$ (left) and $\outsubseq{k}{l}$ (right) rooted at $A$ \\
$\mtip(i,l,A)$ & Inside weight for $\outsubseq{i}{l}$ rooted at $A$ \\
$B,C,U,V,X,Y$ & Labels (or terminal strings) at nodes of the Newick tree $((U,((V,\beta,W)C),X)B)\alpha$ \\
$u,v,x,y$ & Special symbols for $U,V,X,Y$ when they are terminal strings \\
\end{tabular}

>>>>

\noindent
\begin{tabular}{ll}
Symbol & Meaning \\
\hline
$\grammar$ & Grammar \\
$\nodelabels$ & Set of node labels \\
$\terminals$ & Set of terminals \\
$\rules$ & Set of transformation rules \\
$\rulesubset{n}{A}$ & Set of transformation rules of type $n$ (see \tabref{RuleTypes}) whose LHS is $((\beta)A)\alpha$ \\
$\alpha,\beta$ & Arbitrary ordered node-labeled trees \\
$\weight$ & Rule weight function \\
$\seqweight{\alpha}{\outseq}$ & Sum, over derivations of $\outseq$ from $\alpha$, of product over derivation rule weights \\
$\epsilon$ & The empty string \\
$\terminals^\ast$ & Set of strings over $\terminals$, including the empty string \\
$\outseq$ & Output sequence \\
$|\outseq|$ & Length of $\outseq$ \\
$i,j,k,l$ & Integer co-ordinates on $\outseq$, with $1 \leq i \leq j \leq k \leq l \leq |\outseq|$ \\
$m,n$ & Integer co-ordinates on $\outseq$, with $i \leq m \leq j$ and $k \leq n \leq l$ \\
$\outerlen, \innerlen$ & Integer lengths of $\outseq$-subsequences, with $0 \leq \innerlen = (k-j) \leq \outerlen = (l-i) \leq |\outseq|$ \\
$\outsubseq{i}{i}$ & The empty string \\
$\outsubseq{i}{j}$ & (For $j > i$) Substring of $\outseq$ from $i$ to $j-1$ inclusive \\
$\match(i,j,x)$ & Indicates if rule string $x$ matches output string $\outsubseq{i}{j}$ \\
$\fmatch(i,x)$ & Indicates if rule string $x$ matches output string $\outseq$, starting at position $i$ \\
$\rmatch(j,y)$ & Indicates if rule string $y$ matches output string $\outseq$, ending before position $j$ \\
$\iumatch,\jvmatch,\kxmatch,\lymatch$ & Rule string matchers; $\match_{ns}$ matches string $s$ ending/starting at position $n$ \\
$\m(i,j,k,l,A)$ & Inside weight for $\outsubseq{i}{j}$ (left) and $\outsubseq{k}{l}$ (right) rooted at $A$ \\
$\mtip(i,l,A)$ & Inside weight for $\outsubseq{i}{l}$ rooted at $A$ \\
$B,C,U,V,X,Y$ & Labels (or terminal strings) at nodes of the Newick tree $((U,((V,\beta,W)C),X)B)\alpha$ \\
$u,v,x,y$ & Special symbols for $U,V,X,Y$ when they are terminal strings \\
\end{tabular}
